From physical principles to ???

### 2015-10-22 2015CompleteDerivation/completeDerivation.tex
Reviewed counter and styles for assump/defn/prop

\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem*{assump1}{Infinite reducibility (or classical) assumption}
\newtheorem*{assump2}{Determinism and Reversibility assumption}
\newtheorem*{assump3}{Kinematic equivalence assumption}

\newenvironment{rationale}{\textbf{Rationale}.}{$\Box$}
\newenvironment{justification}{\textbf{Justification}.}{$\Box$}
\renewenvironment{proof}{\textbf{Proof}.}{$\Box$}

@@

\begin{assump2}
The state of the physical system under study undergoes deterministic and reversible evolution.
\end{assump2}

@@

\begin{assump1}\label{classical}
The system is infinitely reducible: it can be thought of as composed of two or more similar but smaller systems, each in its own configuration state, which in turn can be thought of as composed of two or more, ad infinitum. We call \emph{particle} such an infinitesimal part.
\end{assump1}

>>>>

\newtheorem{assump}{Assumption}
\renewcommand*{\theassump}{\Roman{assump}}
\newtheorem{prop}{Proposition}[section]

\theoremstyle{definition}
\newtheorem{defn}[prop]{Definition}

\newenvironment{rationale}{\emph{Rationale}.}{$\Box$}
\newenvironment{justification}{\emph{Justification}.}{$\Box$}
\renewenvironment{proof}{\emph{Proof}.}{$\Box$}

@@

\begin{assump}[Determinism and reversability]
The state of the physical system under study undergoes deterministic and reversible evolution.
\end{assump}

@@

\begin{assump}[Infinite reducibility or Classical]\label{classical}
The system is infinitely reducible: it can be thought of as composed of two or more similar but smaller systems, each in its own configuration state, which in turn can be thought of as composed of two or more, ad infinitum. We call \emph{particle} such an infinitesimal part.
\end{assump}
